Characterizing Stellar Streams by ML

### 2023-08-14 src/tex/ms.tex
[showyourwork] overleaf sync

            We implement a hard bound on the range of all parameters.
            Hard cutoffs can be an unwise choice of prior, but we set the ranges to larger than the data prefers and check that the trained parameters are never ``up against" the bounds.
            This makes the priors safe.
            We require these priors for training the neural network. It helps to have a well-bounded problem. Simple hard priors have advantages and disadvantages in this regard.
            An advantage is that in the allowed region the prior does not not contribute to the posterior at all. We don't want it to. We want to keep the posterior as simple as possible, driven as much as possible by the likelihood and not any priors.

>>>>

            We implement a hard bound on the range of all parameters.
            Hard cutoffs can be an unwise choice of prior, but we set the ranges to larger than the data prefers and check that the trained parameters are never ``up against" the bounds.
            This makes the priors safe.
            We require these priors for training the neural network. It helps to have a well-bounded problem. Simple hard priors have advantages and disadvantages in this regard.
            An advantage is that in the allowed region the prior does not not contribute to the posterior at all. We don't want it to. We want to keep the posterior as simple as possible, driven as much as possible by the likelihood and not any priors.
            A marked disadvantage is that outside the bounded region the prior does not contribute a gradient to the loss function the optimizer can use in the fitting.
            However, we sidestep this issue by encoding the prior bounds into the ``geometry" \TODO{(What is this called?)} of the neural network, so that the network can never
            produce outputs outside the hard bounds. This is a standard technique in ML to ensure that the nerual network is efficient, only covering the required region of the output space
